```{r}
library(tidyverse)
library(leaflet)
library(janitor)
library(htmltools)
library(lubridate)

```

#Read the data in. 
```{r}
netflix_movie <- read_csv("../clean_data/netflix_movie.csv")
netflix_tv <- read_csv("../clean_data/netflix_tv.csv")
```

```{r}
str(netflix_movie)
str(netflix_tv)
```
# Number of movies by country.
```{r}
netflix_movie %>% 
  group_by(country) %>% 
  summarise(num_of_movies = n()) %>% 
  arrange(desc(num_of_movies))
```
#Plot
```{r}
netflix_movie %>% 
  group_by(country) %>% 
  summarise(num_of_movies = n()) %>% 
  arrange(desc(num_of_movies)) %>% 
  top_n(10) %>% 
  filter(country !="Unknown") %>% 
  ggplot() +
  aes( reorder(country,num_of_movies),num_of_movies) +
  geom_col(fill = "red")+
  coord_flip() +
  scale_y_continuous(breaks = seq(0,1800,100))

```

#Number of tv series by country,
```{r}
netflix_tv %>% 
  group_by(country) %>% 
  summarise(num_of_tvseries = n()) %>% 
  arrange(desc(num_of_tvseries))
```
#Plot TV
```{r}
netflix_tv %>% 
  group_by(country) %>% 
  summarise(num_of_tvseries = n()) %>% 
  arrange(desc(num_of_tvseries)) %>% 
  top_n(10) %>% 
  filter(country !="Unknown") %>% 
  ggplot()+
  aes(reorder(country, num_of_tvseries) ,num_of_tvseries)+
  geom_col(fill = "red")+
  coord_flip() +
  scale_y_continuous(breaks = seq(0,600,100))

```



#Number of titles.
```{r}
head(netflix_movie)
n_distinct(netflix_movie$title)
```
```{r}
n_distinct(netflix_tv$title)
```
# Number of directors
```{r}
n_distinct(netflix_movie$director)-1 # -1 for the Unknown
```
#Number of countries
```{r}
n_distinct(netflix_movie$country)- 1 #-1 for the Unknown. Count includes International movies. 
```
```{r}
n_distinct(netflix_tv$country)-1 #-1 for the Unknown. Count includes International movies.
```
# Number or ratings for tvs and movies.
```{r}
n_distinct(netflix_movie$rating)
```
```{r}
n_distinct(netflix_tv$rating)

```
#Movie Tv-series duration breakdown
```{r}
netflix_movie %>% 
  summarise(mean_time = mean(duratiom_min, na.rm = T),
            median_time = median(duratiom_min,na.rm = T),
            min_time = min(duratiom_min,na.rm = T),
            max_time = max(duratiom_min, na.rm = T))
```

```{r}
netflix_tv %>% 
  summarise(mean_seasons = mean(number_of_seasons, na.rm = T),
            median_seasons = median(number_of_seasons,na.rm = T),
            min_seasons = min(number_of_seasons,na.rm = T),
            max_seasons = max(number_of_seasons, na.rm = T))

```
#Most popular director in movies
```{r}
netflix_movie %>%
  filter(director != "Unknown") %>% 
  group_by(director) %>% 
  summarise(total = n()) %>% 
  arrange(desc(total)) %>% 
  top_n(20) 

```
#Plot
```{r}
netflix_movie %>% 
  group_by(director) %>% 
  summarise(total = n()) %>% 
  arrange(desc(total)) %>% 
  top_n(10) %>% 
  filter(director !="Unknown") %>% 
  ggplot()+
  aes(reorder(director,total),total)+
  geom_col(fill = "red")+
  coord_flip() +
  scale_y_continuous(breaks = seq(0,20,2))

```


#Number of releases per year 
```{r}
netflix_tv %>% 
  group_by(release_year) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year))
```
#Plot TV
```{r}
netflix_tv %>% 
  group_by(release_year) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year)) %>% 
  ggplot()+
  aes(release_year,num_per_year)+
  geom_col(fill = "red")+
  scale_y_continuous(breaks = seq(0,500,50))

```

#Plot Movies
```{r}
netflix_movie %>% 
  group_by(release_year) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year)) %>% 
  ggplot()+
  aes(release_year,num_per_year)+
  geom_col(fill = "red") +
  scale_y_continuous(breaks = seq(0,700,100))

```



```{r}
netflix_movie %>% 
  group_by(release_year) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year))
```
#Number of movies/shows added by year
```{r}
netflix_movie %>% 
  group_by(year(date_added)) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year))
```
#Plot movie
```{r}
netflix_movie %>% 
  mutate(year_added=year(date_added)) %>% 
  group_by(year_added) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year)) %>% 
  ggplot()+
  aes(year_added,num_per_year)+
  geom_col(fill = "red")+
  scale_x_continuous(breaks = 2008:2020) +
  scale_y_continuous(breaks = seq(0,1800,100))
```


# Unwanted NA CHeck it out 
```{r}
netflix_tv %>% 
  filter(!is.na(year(date_added))) %>% 
  group_by(year(date_added)) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year))
```
#Plot Tv
```{r}
netflix_tv %>% 
  mutate(year_added=year(date_added)) %>% 
  group_by(year_added,country) %>% 
  summarise(num_per_year = n()) %>% 
  arrange(desc(num_per_year)) %>% 
  ggplot()+
  aes(year_added,num_per_year)+
  geom_col(fill = "red") +
  scale_x_continuous(breaks = 2008:2020)+
  scale_y_continuous(breaks = seq(0,850,100))

```

#Number of movies by category
```{r}
netflix_movie %>% 
  group_by(rating) %>% 
  summarise(total_movies = n()) %>% 
  arrange(desc(total_movies))
```
#Plot Movie
```{r}
netflix_movie %>% 
  group_by(rating) %>% 
  summarise(total_movies = n()) %>% 
  arrange(desc(total_movies)) %>% 
  ggplot()+
  aes(reorder(rating,total_movies),total_movies)+
  geom_col(fill = "red")+
  coord_flip()+
  scale_y_continuous(breaks = seq(0,1700,100))

```

```{r}
netflix_tv %>% 
  group_by(rating) %>% 
  summarise(total_movies = n()) %>% 
  arrange(desc(total_movies))
```
#Plot Tv
```{r}
netflix_tv %>% 
  group_by(rating) %>% 
  summarise(total_movies = n()) %>% 
  arrange(desc(total_movies)) %>% 
  ggplot()+
  aes(reorder(rating,total_movies),total_movies)+
  geom_col(fill = "red")+
  coord_flip()+
  scale_y_continuous(breaks = seq(0,700,by = 50))
```
# Map 


```{r}
country <- unique(netflix_tv$country)
```



Read in geodata
```{r}
c_coord <- read_csv("../raw_data/datasets_25827_32914_countries.csv")

```


Cleaning names
```{r}
c_coord <- c_coord %>% clean_names()
```
# geocodes not present for South Korea, Russia West Germany. 
```{r}
netflix_movie %>% 
  filter(country != "International", country != "Unknown") %>% 
  left_join(c_coord) %>% 
  filter(is.na(latitude)) %>% distinct(country) 
```

# Fixing missing values
```{r}
c_coord <- c_coord %>% 
  mutate(country = replace(country, country == "Russian Federation","Russia")) %>% 
  mutate(country = replace(country, country == "Korea, Republic of","South Korea")) 

```

```{r}
netflix_movie <- netflix_movie %>% 
  mutate(country = replace(country, country =="West Germany", "Germany"))
```
# Deleting rowa with country == International and country == Unknown and joining with c-coord.
```{r}
netflix_movie_map <- netflix_movie %>%
  filter(country != "International", country != "Unknown") %>% 
  left_join(c_coord)
```
####Basic map 

# Creating label 
```{r}
netflix_movies_num_country <- netflix_movie_map %>% 
  group_by(country) %>% 
  summarise(num_movies_country = n())
```
```{r}
netflix_movie_map <- netflix_movie_map %>% 
  left_join(netflix_movies_num_country)
```



```{r}
netflix_movie_map$label <- paste("<p>","Country: ",netflix_movie_map$country,"</p>",
                                 "<p>", "Number of movies: ", netflix_movie_map$num_movies_country,"</p>")
```

```{r}
leaflet() %>% 
  addProviderTiles(providers$Stamen.Toner) %>% 
  setView(lat = 22.35335,lng = -16.43312,zoom = 2) %>% 
  addCircleMarkers(
    lng = netflix_movie_map$longitude,
    lat = netflix_movie_map$latitude,
    color = "red",
    weight = 1,
    radius = 5,
    label = lapply(netflix_movie_map$label,HTML))
```









